### 2019-09-23 management.tex
updates management, main

\subsection{Position Responsibilities}
The general and technical chairs are responsible for setting up major milestones and 
ensuring that those milestones are met. Together they oversee all four subcommittees but 
are each primarily in charge of two. They will serve as the primary contacts between subcommittee
chairs and the faculty as well as professionals. The two co-chairs have the final word on all 
conference decisions.
	\item $\large\textbf{\textit{General Co-Chair}}$\\
	In addition to the responsibilities outlined above, the General Co-Chair primarily oversees the
	Non-technical and Publications Subcommittees. Works with the Technical Co-Chair to plan full committee
	meetings and completes any remaining tasks to ensure that milestones are met.
	\item $\large\textbf{\textit{Technical Co-Chair}}$\\
	In addition to the responsibilities outlined above, the Technical Co-Chair primarily oversees the
	Technical and Financial Subcommittees. Works with the General Co-Chair to plan full committee
	meetings and completes any remaining tasks to ensure that milestones are met.

@@

		\item[$\circ$] $\textbf{Logistics Chair (Gavin Davis?)}$\\
		The Logistics Chair is in charge of planning all tours and non-technical workshops and panels. Organizes speakers during dinners
		Also responsible for keeping track of subcommittee and reporting to the General and Technical Co-Chairs.

@@

@@

		\item[$\circ$] $\textbf{Financial Chair}$\\
		Sets the budget for the whole committee and ensures that the committee does not exceed the budget. Manages the ANS Student Committee account and collects receipts. Updates and maintains the budget as required. Keeps track of subcommittee progress and reports to the General and Technical Co-Chairs. 
		\item[$\circ$] $\textbf{Registration Coordinator (Jasmine Dinari?)}$

@@

		Assists the Financial Chair with matters involving sponsorship as well as working closely with the registration coordinator and the General and Technical Co-Chairs.

@@

		\item[$\circ$] $\textbf{Sessions Chair (Gwen Chee?)}$\\

@@

		panels. Also responsible for ensuring that judges understand the judging criteria, and organizes the award ceremony.
		\item[$\circ$] $\textbf{Workshops Coordinator (Zach Jeckell?)}$\\

@@

		\item[$\circ$] $\textbf{Career Fair Coordinator (Rierson Johnson?)}$\\

@@

	\item $\textbf{Communications Subcommittee}$
	The Communications Subcommittee is in charge of public relations and communicating status updates with attendees.
		\item[$\circ$] $\textbf{Publications Chair (Nate Reid?)}$\\
		The Publications Chair is primarily responsible for publishing and organizing the student abstracts, as well as 
		helping the media coordinator maintain a social media presence. 
		\item[$\circ$] $\textbf{Media Coordinator (Nathan Ryan?)}$\\

@@

		\item[$\circ$] $\textbf{Program Coordinator (Brady Moran?)}$\\
		The Program Coordinator is in charge of setting the program for the conference, minimizing event overlap, and coordinating
		with the Publications Chair and Media Coordinator.

@@

>>>>

\subsection{Position Responsibilities}
The three co-chairs are responsible for setting up major milestones and 
ensuring that those milestones are met. Together they oversee all three subcommittees but 
are each primarily in charge of one. They will serve as the primary contacts between subcommittee
chairs and the faculty as well as professionals. The co-chairs have the final word on all 
conference decisions. They serve as the face of the conference and

\begin{itemize}
	\item $\large\textbf{\textit{General Co-Chair}}$\\
	In addition to the responsibilities outlined above, the General Co-Chair primarily oversees the
	Non-technical Subcommittee and the Media Coordinator. He works with the Technical Co-Chair to plan full committee
	meetings and completes any remaining tasks to ensure that milestones are met.
	\item $\large\textbf{\textit{Technical Co-Chair}}$\\
	In addition to the responsibilities outlined above, the Technical Co-Chair primarily oversees the
	Technical Subcommittee. Works with the General Co-Chair to plan full committee meetings and completes any remaining tasks to ensure that milestones are met.
	\item $\large\textbf{\textit{Financial Co-Chair}}$\\
	In addition to the responsibilities outlined above, the Financial Co-Chair primarily oversees the Financial Subcommittee. The Financial Co-Chair is also responsible for interacting with businesses, the university, and ANS National for sponsorship needs. He completes any remaining tasks to ensure that milestones are met.

@@

		\item[$\circ$] $\textbf{Logistics Chair}$\\
		The Logistics Chair is in charge of planning all tours and non-technical workshops and panels. Organizes speakers during dinners. Recruits student volunteers to staff events and sessions during the conference.
		Also responsible for keeping track of the subcommittee and reporting to the Co-Chairs.

@@

		\item[$\circ$]$\textbf{Tours Coordinator}$\\
		The tours coordinator organizes tours and works with the transportation coordinator to ensure that transportation is available during the conference for these tours.
		\item[$\circ$]$\textbf{Program Coordinator}$\\
		The program coordinator creates programs for the conference, sets the conference schedule to minimize overlap between events and increase student involvement. Communicates with other coordinators and subcommittees about the schedule of events. Designs and purchases T-shirts for attendees. Arranges gift bags for attendees. Works with sponsorship coordinator to create gift bags.

@@

		\item[$\circ$] $\textbf{Account Coordinator}$\\
		Manages the ANS Planning Committee account with Busey Bank and ANS National. The account coordinator is also responsible for keeping track of receipts, setting a budget for the committee, keeps track of all transactions, 
		\item[$\circ$] $\textbf{Registration Coordinator }$

@@

		Assists the Financial Co-Chair with matters involving sponsorship as well as working closely with the Registration and Account Coordinators and the General and Technical Co-Chairs. Works with the Program Coordinator on gift bag items and works with the Career Fair Coordinator.

@@

		\item[$\circ$] $\textbf{Technical Subcommittee Chair}$\\
		 Also responsible for ensuring that judges understand the judging criteria, and organizes the award ceremony.
		\item[$\circ$] $\textbf{Sessions Coordinator}$\\

@@

		panels. Makes sure that all rooms are properly set up with equipment to ensure smooth technical sessions.
		\item[$\circ$] $\textbf{Workshops Coordinator}$\\

@@

		\item[$\circ$] $\textbf{Career Fair Coordinator}$\\

@@

	\item $\textbf{Media Coordinator}$\\

@@

@@

$\textbf{Financial Co-Chair}$\\\\

$\textbf{Account Coordinator}$\\
$\textbf{Registration Coordinator}$\\
$\textbf{Sponsorship Coordinator}$\\

$\textbf{Technical Subcommittee}$\\\\

$\textbf{Technical Subcommittee Chair}$\\
$\textbf{Sessions Coordinator}$\\
$\textbf{Workshops Coordinator}$\\
$\textbf{Career Fair Coordinator}$\\

$\textbf{Non-Technical Subcommittee}$\\\\

$\textbf{Logistics Chair}$\\
$\textbf{Hotels and Transportation Coordinator}$\\
$\textbf{Hospitality and Catering Coordinator}$\\
$\textbf{Tours Coordinator}$\\
$\textbf{Program Coordinator}$\\

$\textbf{Media Coordinator}$\\
